---
title: "Homework 6"
author: "Marc Mendez & Joel Cantero"
date: "5th May, 2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


First of all, we are going to install and load all the libraries we need for this exercise. The factominer library is needed for the catdes function, which is needed on exercise 2. Then the arules function is needed to the the association rules.


```{r installing-packages, message=FALSE, results=FALSE, warning=FALSE}
packages <- c("FactoMineR", "arules")
for (package in packages) {
    if(!require(package,  character.only=TRUE)){
        install.packages(package, repos="http://cran.rstudio.com")
        library(package,  character.only=TRUE)
    } 
}
```


##1. Read the file: tic_tt.csv. Check the "class"" of every variable of tic_tt.

First of all we need to check the data and we can see that all the variables are booleans or factors with more than 2 levels. So, for loading the data, we will set the classes as factors and set the first one as row names because they are numbers that don't give information to the study. We will make a summary of it and analize all the results to see that the load has been succesfull.
```{r echo=FALSE, warning=FALSE}
tic <- read.csv("tic_tt.csv", sep=";", colClasses = c(rep("factor",33)), row.names=1)
summary(tic)
```
##2. Find the profile of the people who do payments by Internet (use the function catdes of FactoMineR). (to perform the catdes of a variable, it should be categorical (factor in the R nomenclature).
To study the profile of the people who do payments by Internet we are going to execute the catdes function over the variable "Pagament.a.trav.s.d.Internet.". By doing this we can see the variables that have a realtion with this one.
```{r}
a <- catdes(tic, 28)
plot(a)
```
As we can see in this plot the users that make payments through internet use electronic payments services and also they use internet every day. Most of them know English so there is a relation with the language also.
We can see that, on the other hand, people that not pay through internet tend to not have electronic payment services as well as few usage of e-mail. And also they don't speak English, which makes sense as english is the most common language on the computers world. We can notice that there are differences between users that do payments on internet and people that not. 
##3. Convert the tic_tt file to a transactions file.
To do this convestion we will use as() funtion from the library arules. This conversion is to make the association rules after.To do this conversion we needed to delete the first column as it wasn't a factor and have all the other columns as factors.
```{r}
tic.trans <- as(tic, "transactions")
tic.trans

itemFrequency(tic.trans)
```

##4. Define the parameters: Min_support, min_confidence and m??ximum size of itemsets, and run the apriori function.

```{r}
minSupp <- 0.01
minConf <- 0.4
maxSize <- 5
rules <- apriori (tic.trans, parameter = list (support=minSupp, confidence=minConf, maxlen = maxSize))
inspect(rules[1:10])
names(tic_tt)
```

##5. List the 10 most frequent itemsets.
```{r}
fsets <- unique(generatingItemsets(rules))
fsets.df <- as(fsets, "data.frame")
sor.fsets <- fsets.df[order(-fsets.df$support),]
sor.fsets[1:10,]
```

##6. List the first 10 rules sorted by the lift.

```{r}
top10.lift <- inspect(sort(rules, by="lift")[1:10])
```

##7. List the 10 rules according the lift, where the Consequent is "Pagament.a.traves.d.Internet.".

```{r}
rulesConseq <- subset(rules, subset = rhs %in% c("Pagament.a.trav.s.d.Internet.=FALSE") )

top10.lift.Conseq <- inspect(sort(rulesConseq, by="lift")[1:10] )
```